Numerical error propagation in the HCP structural pre-processing pipelines

### 2018-05-02 paper.tex

\usepackage{pdfcomment}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}

@@

\begin{figure}
%  \includegraphics{brain\_classification}
  \includegraphics[scale=0.3]{images/simple_graph}
  \caption{Process graph constructed from an example brain extraction
    script. Every node in the graph is labeled using (1) a process id
    created by our reconstruction, (2) the name of the executable run
    by the process. Processes that read or write temporary files are
    represented with squares; other ones with circles. Plain edges
    represent the process tree (\texttt{fork()} or \texttt{clone()}
    system calls). Dashed edges represent file dependencies: temporary
    files are in yellow and result files are in green.\todo{Add the
      script next to the graph. Remove node colors.}}
  \label{fig:graph-example}
\end{figure}

@@

The process graphs of real pipelines are much larger than the one in 
Figure~\ref{fig:iterations}. To represent such large graphs, we 
summarize them by (1) building subgraphs for every interesting node 
(e.g. red and blue nodes with their children) (2) remove the 
interesting nodes from graph (3) finding largest connected components 
in the remaining nodes (iteratively).

@@

Figure \ref{fig:2} shows the annotated provenance graph of the
PreFreeSurfer pipeline executed on CentOS6 and CentOS7.  Processes
that created errors are shown in red, processes that removed errors
are in blue, and other processes are in green.  Squares denote
processes for which the classification is uncertain, due to temporary
files that were removed during the execution. Black edges link
sub-processes to their parents while dashed edges denote file
dependencies between processes (green edges: files with no errors; red
edges: files with errors; yellow edges: temporary files).  The
processes that introduce errors in PreFreeSurfer are: linear
registration with “\emph{FLIRT}” (8 occurrences, in ACPC Alignment,
BrainExtraction, DistortionCorrection, AtlasRegistration), non-linear
registration with “\emph{FNIRT}” (3 occurrences, in BrainExtraction
and AltasRegistration), image warping with “\emph{new\_invwarp}” (3
occurrences, in BrainExtraction and AtlasRegistration).  In addition,
errors were observed in image mean and standard-deviation computations
with “\emph{fslstats}” (3 occurrences in BiasFieldCorrection), and in
masked image extrapolation with “\emph{fslmaths}” (1 occurrence, in
BiasFieldCorrection).  Besides, transformation format conversion with
“\emph{convertwarp}” (2 occurrences, in DistortionCorrection) was able
to remove errors.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{images/graph}
  \caption{An annotated provenance graph from the PreFreesurfer pipeline. Processes that created errors are in red. 
Full-resolution image available at \url{https://drive.google.com/open?id=174yyn8SuVOUcK5aRVw0bagjDanLD0FLt}.}
  \label{fig:2}
\end{figure}

>>>>

\usepackage{pdfcomment}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{caption}
\usepackage{listings}
\usepackage{verbatim}

@@

\medskip
\noindent
\begin{minipage}[]{.5\linewidth}
  \centering
  \includegraphics[scale=0.2,width=.4\linewidth]{images/simple_graph}
%  \captionof{figure}{This is a figure caption.} \label{myfig1}
\end{minipage}
\begin{minipage}[]{.3\linewidth}
\small\captionof{algorithm}{sample script of a process graph}\label{sample_script}
{\scriptsize
\begin{verbatim}
#!/bin/bash
if [ # !=1 ]
then
    echo "usage: 0 <inputimage.nii.gz>"
    exit 1
fi
input_image=$1
bet_output="$(basename ${input_image} .nii.gz)_brain.nii.gz"
bet_output_binarized="$(basename ${input_image} .nii.gz)_brain_bin.nii.gz"

bet ${input_image} ${bet_output} > bet_temp.out
echo "Voxels / Volume in brain mask:"
fslstats ${bet_output} -V
fslmaths ${bet_output} ${bet_output_binarized}
echo "Voxels / Volum in binarized brain mask:"
\rm bet_temp.out
\end{verbatim}
}
\end{minipage}
\captionof{figure}{Process graph constructed from an example brain extraction
    script. Every node in the graph is labeled using (1) a process id
    created by our reconstruction, (2) the name of the executable run
    by the process. Processes that read or write temporary files are
    represented with squares; other ones with circles. Plain edges
    represent the process tree (\texttt{fork()} or \texttt{clone()}
    system calls). Dashed edges represent file dependencies: temporary
    files are in yellow and result files are in green.} \label{myfig1}
\medskip

@@

The process graphs of real pipelines are much larger than the one in 
Figure~\ref{fig:iterations}. To represent such large graphs, we 
summarize them by (1) building subgraphs for every interesting node 
(e.g. red and blue nodes with their children) (2) building connected components 
in the absence of interesting nodes for the remaining nodes in the process graph. 
Each node in the summarized graph represent either a shrinked interesting subgraph or 
connected component and edges represent any connection between two shrinked nodes.

@@

Figure \ref{fig:summarized-graph} shows the annotated provenance graph of the
PreFreeSurfer pipeline executed on CentOS6 and CentOS7.  Processes
that created errors are shown in red, processes that removed errors
are in blue, and other processes are in green.  Squares denote
processes for which the classification is uncertain, due to temporary
files that were removed during the execution. Black edges link
sub-processes to their parents while dashed edges denote file
dependencies between processes (green edges: files with no errors; red
edges: files with errors; yellow edges: temporary files).  The
processes that introduce errors in PreFreeSurfer are: linear
registration with “\emph{FLIRT}” (8 occurrences, in ACPC Alignment,
BrainExtraction, DistortionCorrection, AtlasRegistration), non-linear
registration with “\emph{FNIRT}” (3 occurrences, in BrainExtraction
and AltasRegistration), image warping with “\emph{new\_invwarp}” (3
occurrences, in BrainExtraction and AtlasRegistration).  In addition,
errors were observed in image mean and standard-deviation computations
with “\emph{fslstats}” (3 occurrences in BiasFieldCorrection), and in
masked image extrapolation with “\emph{fslmaths}” (1 occurrence, in
BiasFieldCorrection).  Besides, transformation format conversion with
“\emph{convertwarp}” (2 occurrences, in DistortionCorrection) was able
to remove errors.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{images/summarized_graph}
  \caption{An annotated summarized process graph from the PreFreesurfer pipeline.
Each node in the graph is represented in red, blue or green colors and is labeled 
using the name of the executable run by the interesting process. The close up nodes 
reveal each shrinked subgraph in details.}
  \label{fig:summarized-graph}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{images/graph}
  \caption{A complete process graph from the PreFreesurfer pipeline.
Full-resolution image available at \url{https://drive.google.com/open?id=174yyn8SuVOUcK5aRVw0bagjDanLD0FLt}.}
  \label{fig:complete-graph}
\end{figure}
